### 2017-11-11 vipassana-for-hackers.tex
switching from pdflatex to xelatex... hopefully this does not ruin too many things

@@

\begin{center}
  \LARGE{Habit's Exception: Sankhara}
\end{center}

The notion of Sankhara can be split into two camps, in terms of its definition and use. The first, the notion that the body and mind contain ``impurities'' and that the objective of meditation is to rid the body-mind of such impurities, will be excluded from all discussion here. The second, more common use of the term ``Sankhara'' refers to ``conditioned phenomena'' or ``mental dispositions''. The Hindi word, संस्कार (``sanskaar'') roughly translates in this context to ``impression''. This second definition will apply to this paper.

Here, we might choose a more specific term from Psychology: habits. Sankharas, as far as this document is concerned, can be thought of as the ingrained habits of the brain and nervous system. Some concrete examples include liking (or disliking) the taste of olives, my body's ability to type at this QWERTY keyboard without consciously considering each keystroke, and the physical and emotional response I have to news of violence in my city of residence.

@@

Put more succinctly, your activities will include: Eat, sleep, poop, bath, meditate.\\

That's it.\\

>>>>

\usepackage{polyglossia}
\setdefaultlanguage{english}
\setotherlanguage{sanskrit}
\usepackage{fontspec}
\newfontfamily\devanagarifont[Scale=MatchUppercase]{Kohinoor Devanagari}

@@

\begin{center}
  \LARGE{Habit's Exception: Saṅkhāra}
\end{center}

The notion represented by the Pali word \textit{Saṅkhāra} can be split into two camps, in terms of its definition and use. The first, the notion that the body and mind contain ``impurities'' and that the objective of meditation is to rid the body-mind of such impurities, will be excluded from all discussion here. The second, more common use of the term ``Sankhara'' refers to ``conditioned phenomena'' or ``psychological dispositions''. The equivalent Hindi/Sanskrit word, \foreignlanguage{sanskrit}{संस्कार} (sanskaar) roughly translates in this context to ``mental impression''. This second definition will apply to this paper.

Here, we might choose a more specific term from Psychology: habits. Saṅkhāras, as far as this document is concerned, can be thought of as the ingrained habits of the brain and nervous system. Some concrete examples include liking (or disliking) the taste of olives, my body's ability to type at this QWERTY keyboard without consciously considering each keystroke, and the physical and emotional response I have to news of violence in my city of residence.

@@

Put more succinctly, your activities will include: Eat, sleep, poop, bath, meditate.

That's it.
